---
title: "Data Wrangling (Data Preprocessing)"
author: "Jeremy Jian Zhi Chia"
subtitle: Practical assessment 1
date: "11/08/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---


## **Setup**

```{r}

# Load the necessary packages required to reproduce the report. For example:

library(kableExtra)
library(magrittr)
library(dplyr)
library(readr)
library(tidyr)
library(knitr)


```


## **Student names, numbers and percentage of contributions**
```{r, echo=FALSE}

# Add your names, numbers and percentage of your contribution here.

na<- c("Jeremy Jian Zhi Chia")
no<- c("3917515")
pc<- c("100%")

s<- data.frame(cbind(na,no,pc))
colnames(s)<- c("Student name", "Student number", "Percentage of contribution")

s %>% kbl(caption = "Group information") %>%
  kable_classic(full_width = F, html_font = "Cambria")




```

## **Data Description**

* This dataset consists of all Netflix original films, documentaries and specials released as of June 1st, 2021.
* The creator of this dataset web scraped the data from Wikipedia and integrated it with another dataset consisting of all their corresponding IMDB scores.
* URL of dataset: https://www.kaggle.com/luiscorter/netflix-original-films-imdb-scores/version/1

### **Variables of Dataset**

* Title of the Film
* Genre of the Film
* Original Premiere Date
* Runtime (Minutes)
* IMDB Scores (as of 01/06/2021)
* Languages currently Available (as of 01/06/2021)

## **Read/Import Data**

<!-- Read/Import the data into R, then save it as a data frame. You can use Base R functions or readr, xlsx, readxl, foreign, rvest packages for this purpose. In this step, you must provide the R codes with outputs (i.e. head of data set) and explain everything that you do in order to import/read/scrape the data set. You can provide the R codes with outputs using R chunks like this: -->

```{r}

# Import dataset
netflix <- read_csv("NetflixOriginals.csv")

# Check first few rows of imported dataset
head(netflix)

```

The dataset is imported using readr's read_csv() function. The imported dataset has a data structure of a tibble. The columns and first few rows of the dataset is then inspected using R's base function head().

## **Inspect and Understand**


```{r}

# Inspect structure of data
str(netflix)

```

The output above displays all the variables and their data types. The Title, Genre, Premiere and Language columns are detected by R as characters as they contain strings in the observations. Runtime and IMDB Score columns are detected as numerical data as they contain numbers within the data.

```{r}

# Convert premiere column's data type
netflix$Premiere <- as.Date(netflix$Premiere, format ="%B %d, %Y")
head(netflix$Premiere)

```
The Premiere column was initially recognised as a character data type. The above code converts this character into a date format, which allows for any time-series analysis to be done if needed.

```{r}

# Convert Runtime column's data type
netflix$Runtime <- as.integer(netflix$Runtime)
class(netflix$Runtime)

```
As the values in the Runtime column only take integers and not values with decimals, it is then converted from a double variable into an integer.

```{r}

# Inspect structure of data after conversions
str(netflix)

```
From the above output, it can be seen that the data types for the Premiere and Runtime column has been changed to Date and Integer respectively.

## **Subsetting** 

<!-- Subset the data frame using the first 10 observations (include all variables). Then convert it to a matrix. Check the structure of that matrix (i.e. check whether the matrix is a character, numeric, integer, factor, or logical) and explain in a few words why you ended up with that structure. Provide the R codes with outputs and explain everything that you do in this step. -->



```{r}

# Subset your data and convert it to a matrix, provide R codes here.


```

Provide explanations here.


## **Create a new Data Frame**

<!-- You will create a new data frame from scratch. Note that, this step is independent from the dataset that you used in the previous steps.  -->

<!-- In this step you should: -->

<!-- * Create a data frame from scratch with 2 variables and 10 observations. Your data frame has to contain one integer variable and one ordinal variable. Make sure that you factorised and ordered the ordinal variable properly. Show the structure of your variables and the levels of the ordinal variable. -->

<!-- * Create another numeric vector and use cbind() to add this vector to your data frame. After this step you should have 3 variables in the data frame.  -->


<!-- * Provide the R codes with outputs and explain everything that you do in this step.  -->


```{r}

# Create a new data frame, provide R codes here.


```

Provide explanations here.

<!-- ## IMPORTANT NOTE:  -->

<!-- The report must be uploaded to Assessment 1 section in Canvas as a **PDF** document with R codes and outputs showing. The easiest way to achieve this is to run all R chunks first, then **Preview** your notebook in **HTML** (by clicking Preview), then **Open in Browser (Chrome)**, then **Right Click on the report in Chrome** , then **Click Print** and Select the Destination Option to **Save as PDF**. Upload this PDF report as one single file via the Assessment 1 page in CANVAS. -->



<!-- **DELETE the instructional text provided in the template. Failure to do this will INCREASE the SIMILARITY INDEX reported in TURNITIN** If you have any questions regarding the Assessment instructions and the R template, please post it on the discussion board.  -->

<br>
<br>
